---
title: "Task3"
author: "Polishchuk Oleksandr"
date: "11/12/2024"
format:
  html:
    embed-resources: true
editor: source
---

## Question 1 title

Question description

```{r}
library(dplyr)

# Now you can use the pipe operator
airquality %>%
  filter(Ozone > 29 & Temp > 59)
```


## Question 2 title

Question description

```{r}
# Load the airquality dataset
airquality <- airquality

# 1. What are the column names``` of the data frame?
colnames(airquality)

# 2. What are the row names of the data frame?
rownames(airquality)

# 3. Extract the first 6 rows of the data frame and print them to the console
head(airquality, 6)

# 4. How many observations (i.e. rows) are in this data frame?
nrow(airquality)

# 5. Extract the last 6 rows of the data frame and print them to the console
tail(airquality, 6)

# 6. How many missing values are in the "Ozone" column of this data frame?
sum(is.na(airquality$Ozone))

# 7. What is the mean of the "Ozone" column in this dataset? Exclude missing values (coded as NA) from this calculation.
mean(airquality$Ozone, na.rm = TRUE)

# 8. Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90.
filtered_data <- airquality %>%
  filter(Ozone > 29 & Temp > 59)

filtered_data
```

